%-------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------------------------------------------

\documentclass{techresume} % Use the custom resume.cls style

\usepackage{enumitem}
\usepackage[left=0.5in,top=0.4in,right=0.5in,bottom=0.5in]{geometry}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{BIN XUAN KONG} % Your name
\address{(+60)126112151 \\ binxuankong@gmail.com \\ github.com/binxuankong}

\begin{document}

%-------------------------------------------------------------------------------------
%	PROFILE SUMMARY
%-------------------------------------------------------------------------------------

\begin{rSection}{Profile Summary}

Data Science practitioner with 5+ years of experience delivering end-to-end AI/ML systems, specializing in GenAI, LLM applications, applied machine learning, MLOps, and large-scale data product development. Proven track record of architecting and deploying award-winning GenAI products, leading cross-functional delivery, and scaling ML systems in production environments across fintech, healthtech, and enterprise domains.

\end{rSection}

%-------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%-------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Leadership & Technical leadership, AI product direction, cross-functional alignment, \\
& stakeholder management, roadmap ownership \\
AI/ML & Supervised \& Unsupervised Learning, GenAI/LLMs, RAG, NLP, Computer Vision, \\
& Recommendation Systems, Multi‑Agent Systems \\
MLOps & AWS (ECS/EC2/Lambda), Terraform, CI/CD, Airflow, Docker, Kubernetes, dbt \\
Programming & Python, SQL, Java, NumPy, Pandas, Scikit-Learn, PyTorch, TensorFlow, Hugging Face \\
Soft Skills & Problem Solving, Ownership, Technical Communication, Mentoring, Fast Delivery \\
Languages & English (Native/Bilingual), Chinese Simplified (Native/Bilingual), Malay (Professional)
\end{tabular}

\end{rSection}

%-------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%-------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\begin{rSubsection}{GXBank}{Jul 2023 - Present}{Data Scientist, Senior Specialist}{Selangor, Malaysia}
    \item Led architecture and end-to-end development of \textbf{AiNi}, a multi-agent GenAI chatbot with secure verification flows, RAG pipelines, and live-agent orchestration. Achieved 47\% automated containment, significantly reducing customer support load.
    \item Designed and built an \textbf{internal GenAI assistant} for customer support, improving knowledge retrieval, accuracy, and response speed.
    \item Led \textbf{VoC360}, a bank-wide voice-of-customer AI insights platform—centralizing unstructured data streams and deploying an insights LLM assistant.
    \item Architected and deployed \textbf{GuardPlus} (rule-based document tampering detection) and \textbf{GuardAI} (GenAI-augmented tampering detection). Improved detection coverage and reduced rule maintenance overhead.
    \item Led design and development of \textbf{GXScan}, a document intelligence engine involving OCR extraction, transaction categorisation, and business legitimacy scoring.
    \item Built \textbf{Customer Lifetime Value (CLV)} and \textbf{churn prediction} models using survival analysis, achieving 93\% ROC on test data.
    \item Delivered ML components for \textbf{AML and name-matching systems}, including improved localized name equivalence models.
    \item Implemented \textbf{content-moderation CV models}, including profanity and inappropriate image scanning.
    \item Partnered with MLOps and SRE teams to productionize ML systems using Terraform, Helm, GitLab CI/CD, Airflow, with strong observability and monitoring.
\end{rSubsection}

\begin{rSubsection}{Naluri}{Jun 2022 - Jun 2023}{Data Scientist}{Kuala Lumpur, Malaysia}
    \item Built segmentation and recommendation systems for digital health coaching, enabling personalized interventions.
    \item Developed predictive models for user health outcome improvements.
    \item Created a computer vision fitness-tracking prototype for exercise repetition counting.
    \item Designed web scrapers and fine-tuned image models for food-image classification.
    \item Managed AWS EC2/ECS infrastructure and ETL pipelines (dbt, Prefect, Redshift).
\end{rSubsection}

\newpage

\begin{rSubsection}{The Center of Applied Data Science (CADS)}{Mar 2020 - Jun 2022}{Data Science Specialist}{Kuala Lumpur, Malaysia}
    \item Designed a multi-source data integration pipeline for analytics.
    \item Developed ML models for sales opportunity prediction on Salesforce data.
    \item Built job/skills/learning recommendation systems deployed as Flask APIs.
    \item Performed large-scale web scraping and text mining for labour-market insights.
\end{rSubsection}

\begin{rSubsection}{Maxis}{Jul 2017 - Aug 2017}{Business Intelligence Intern}{Kuala Lumpur, Malaysia}
    \item Developed Qlik dashboards and performed data extraction using Oracle SQL.
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Imperial College London}{Sep 2018 - Sep 2019}{MSc Advanced Computing}{Result: Distinction}
\end{rSubsection}

\begin{rSubsection}{University of Manchester}{Sep 2015 - Jun 2018}{BSc(Hons) Computer Science and Mathematics}{Classification: First Class}
\end{rSubsection}

\begin{rSubsection}{Taylor's College Subang Jaya}{Jan 2014 - Jun 2015}{Cambridge International A Level}{Chemistry (A*), Physics (A*), Mathematics (A*)}
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------------
%	PROJECTS SECTION
%-------------------------------------------------------------------------------------

\begin{rSection}{Projects}

\begin{rSubsection}{Deep Image Reconstruction from Brain Activity}{Apr 2019 - Sep 2019}{Imperial College London}{}
    \item Built a dual-GAN architecture to reconstruct images from EEG/fMRI signals.
    \item Replicated state-of-the-art CNN inversion methods for evaluation.
\end{rSubsection}

\begin{rSubsection}{Poetry Generation using Deep Learning}{Sep 2017 - Apr 2018}{The University of Manchester}{}
    \item Built RNN/GRU‑based text generation models for topic-based poetry.
\end{rSubsection}
    
\end{rSection}

%-------------------------------------------------------------------------------------
%	ACHIEVEMENTS SECTION
%-------------------------------------------------------------------------------------

\begin{rSection}{Awards and Achievements}

\begin{rSubsection}{Global Retail Banking Innovation Awards 2025}{The Digital Banker}{}{}
    \item Won the \textbf{Outstanding Interactive Chatbot Service by a Digital Bank} and \textbf{Best Gen-AI Chatbot Initiative - By a Neobank} awards for AiNi.
\end{rSubsection}

\begin{rSubsection}{Global AI Innovation Awards 2025}{The Digital Banker}{}{}
    \item Won the \textbf{Outstanding AI Initiative for Financial Inclusion} and \textbf{Outstanding Use of AI for Front Office} awards for AiNi.
\end{rSubsection}

\begin{rSubsection}{Global Retail Banking Innovation Awards 2024}{The Digital Banker}{}{}
    \item Won the \textbf{Outstanding Use of Advanced Analytics} and \textbf{Best Gen-AI Retail Product Initiative} awards for VoC360.
    \item Won the \textbf{Best Data Analytics Initiative} (Highly Acclaimed) award as part of the DSA team.
\end{rSubsection}

\begin{rSubsection}{Asian Banking \& Finance Retail Banking Awards 2024}{Asian Banking \& Finance}{}{}
    \item Won the \textbf{Analytics Initiative of the Year} award as part of the DSA team.
\end{rSubsection}

\begin{rSubsection}{Certificate of Excellence}{The University of Manchester}{}{}
    \item Awarded to the top 10\% of graduating students in the School of Computer Science
\end{rSubsection}

\end{rSection}

%-------------------------------------------------------------------------------------
%	REFERENCE AVAILABLE
%-------------------------------------------------------------------------------------

\sectionskip
\sectionlineskip
\hrule
{\bf References available on request}

\end{document}
